---
title: "Assignment 1"
author: "Nikola Metes"
output:
  pdf_document: default
  html_document:
    df_print: paged
  word_document: default
---
# Set up environment
```{r}
# library(caret)
library("Hmisc")
library(dplyr)
library(ggplot2)
```
```{r}
Data<-file.path("Data")
```
```{r}
d<-read.csv(file.path(Data,"GermanCredit.csv"))
head(d)
```
```{r}
d1<-read.csv(file.path(Data,"GermanCredit_modified_SP19_001.csv"))
head(d1)
```
```{r}
Hmisc::describe(d)
```
```{r}
de <- describe(d)
```
```{r}
# p <- plot(d)
# plot(d, which='categorical') 
```

# Question 1.3.a
This data represents a collection of important variables that a certain financial institution might find important in their processing of financial loans. There are general factors that are mostly represented by numerical values and integers (apart from class) that allow us to 

# Question 1.3.b
In this data set we have 1000 observations and 62 different variables.

# Question 1.3.c
There are 61 numerical variables. 

They are the following: Duration,	Amount,	InstallmentRatePercentage;	ResidenceDuration;	Age;	NumberExistingCredits;	NumberPeopleMaintenance;	Telephone;	ForeignWorker;	CheckingAccountStatus.lt.0;	CheckingAccountStatus.0.to.200;	CheckingAccountStatus.gt.200;	CheckingAccountStatus.none;	CreditHistory.NoCredit.AllPaid;	CreditHistory.ThisBank.AllPaid;	CreditHistory.PaidDuly;	CreditHistory.Delay;	CreditHistory.Critical;	Purpose.NewCar;	Purpose.UsedCar;	Purpose.Furniture.Equipment;	Purpose.Radio.Television;	Purpose.DomesticAppliance;	Purpose.Repairs;	Purpose.Education;	Purpose.Vacation;	Purpose.Retraining;	Purpose.Business;	Purpose.Other;	SavingsAccountBonds.lt.100;	SavingsAccountBonds.100.to.500;	SavingsAccountBonds.500.to.1000;	SavingsAccountBonds.gt.1000;	SavingsAccountBonds.Unknown;	EmploymentDuration.lt.1;	EmploymentDuration.1.to.4;	EmploymentDuration.4.to.7;	EmploymentDuration.gt.7;	EmploymentDuration.Unemployed;	Personal.Male.Divorced.Seperated;	Personal.Female.NotSingle;	Personal.Male.Single;	Personal.Male.Married.Widowed;	Personal.Female.Single;	OtherDebtorsGuarantors.None;	OtherDebtorsGuarantors.CoApplicant;	OtherDebtorsGuarantors.Guarantor;	Property.RealEstate;	Property.Insurance;	Property.CarOther;	Property.Unknown;	OtherInstallmentPlans.Bank;	OtherInstallmentPlans.Stores;	OtherInstallmentPlans.None;	Housing.Rent;	Housing.Own;	Housing.ForFree;	Job.UnemployedUnskilled;	Job.UnskilledResident;	Job.SkilledEmployee;	Job.Management.SelfEmp.HighlyQualified;
 
They represent different numerical values for some (i.e. amount, duration, age), while others are binary (using 1 and 0) displaying if a certain individual has a variable (1) or doesn't have one (0). 

# Question 1.3.d
There is 1 categorical value. The only categorical value is Class. It measures the customers credit as being either Good or Bad.

# Question 1.3.e
We can perform certain calculations and observe patterns and other trends with loan users.This can display different insights (i.e. who is applying for loans, at what age, what is their credit history, their current assets, if they are employed etc.)

```{r}
d %>% 
  ggplot(aes(x=Amount,y=Duration,color=factor(Housing.Own)))+
  geom_point()+
  geom_smooth(method="lm")
```


