---
title: "Assignment 5 - Nikola Metes"
output: html_notebook
---

```{r}
install.packages("rpart")
install.packages("rpart.plot")
```

```{r,include=FALSE}
library(rpart)
library(rpart.plot)
library(tidyverse)
```

# 1 Load the Assignment data
```{r}
# load the data set
GermanCredit <- read_csv(file.path("Data", "GermanCredit_modified_SP19_001.csv"))
```

```{r}
# Split data into train and test
 set.seed(737900)

# set an index to split the data set  
# 
# Create the train data frame
s <- sample(nrow(GermanCredit), replace=FALSE, size = .8*nrow(GermanCredit)) 
trainDF <- GermanCredit[s,]
# 
# Create the test data frame  
testDF <- GermanCredit[-s,]
# 
```


# 2.1 Build an Initial Classification Tree
```{r}
tree.1 <- rpart(formula=Class~.,data=trainDF,
                control=rpart.control(cp=0,minsplit=30,xval=10))
```
#Plot the fitted tree.1.
```{r}
pdf("treeplot.pdf")
rpart.plot(tree.1, box.palette="RdBu", shadow.col="gray", nn=TRUE)
dev.off()
```

# Describe in your own words, the root node for this decision tree.
The first split between Checking from 0 to 200, or is less than 0. 
The two levels 0. to 200. and None were split to the left and the

# What does it mean?
The split checking 0 to 200 has a slightly higher proportion than those who have checking

# What percent of cases in the training set are accurately identified as “Good” credit by this single decision node alone?
If it is Yes then it goes to a 54% Good, if it is No then it goes to a 46% Good.

# How many internal nodes (not including the root node) are there in this tree?
not counting the leafs, there are 17 nodes

# How many leaf nodes?
19 leaf nodes
