---
title: "R Notebook"
output: html_notebook
---

```{r,include=FALSE}
install.packages("tidyverse")
install.packages("car")
```
```{r}
library(tidyverse)
library(car)
```
```{r}
# load the data set
GermanCredit <- read_csv(file.path("Data", "GermanCredit_modified_SP19_001.csv")) %>% 
  mutate(good=if_else(Class=="Good",1,0)) %>% 
  select(-Class)
```

```{r}
# Split data into train and test
 set.seed(737900)

# set an index to split the data set  
# 
# Create the train data frame
s <- sample(nrow(GermanCredit), replace=FALSE, size = .8*nrow(GermanCredit)) 
trainDF <- GermanCredit[s,]
# 
# Create the test data frame  
testDF <- GermanCredit[-s,]
# 
```
2 Fit a logistic regression model in R
Fit a logistic regression model to predict the Class variable using all of the predictors in trainDF and assign the fitted model to the object logit.fit1.

MISSING CODE

```{r}
str(GermanCredit)
trainDF %>% select(Class) %>% table()
```

```{r}
logit.fit1 <- glm(good~.,family=binomial,data=trainDF)
Anova(logit.fit1)
```


```{r}
logit.fit1 <- trainDF %>% 
  select(-ResidenceDuration) %>% 
  glm(good~.,family=binomial,data=.)
Anova(logit.fit1)
```
```{r}
logit.fit1 <- trainDF %>% 
  select(-ResidenceDuration,-Age) %>% 
  glm(good~.,family=binomial,data=.)
Anova(logit.fit1)
```
```{r}
logit.fit1 <- testDF %>% 
  select (-ResidenceDuration, -Age, -Job.Type) %>% 
  glm(good~.,family=binomial,data=.)
Anova(logit.fit1)
  
```
```{r}
logit.fit1 <- testDF %>% 
  select (-ResidenceDuration, - Age, -Job.Type, -NumberPeopleMaintenance) %>% 
  glm(good~.,family=binomial,data=.)
Anova(logit.fit1)
```

```{r}
logit.fit1 <- testDF %>% 
  select (-ResidenceDuration, -Age, -Job.Type, -NumberPeopleMaintenance, -Telephone) %>% 
  glm(good~.,family=binomial,data=.)
Anova(logit.fit1)
```

```{r}
logit.fit1 <- testDF %>% 
  select (-ResidenceDuration, -Age, -Job.Type, -NumberPeopleMaintenance, -Telephone, -NumberExistingCredits) %>% 
  glm(good~.,family=binomial,data=.)
Anova(logit.fit1)
```
```{r}
logit.fit1 <- testDF %>% 
  select (-ResidenceDuration, -Age, -Job.Type, -NumberPeopleMaintenance, -Telephone, -NumberExistingCredits, -Other.Debtors) %>% 
  glm(good~.,family=binomial,data=.)
Anova(logit.fit1)
```
```{r}
logit.fit1 <- testDF %>% 
  select (-ResidenceDuration, -Age, -Job.Type, -NumberPeopleMaintenance, -Telephone, -NumberExistingCredits, -Other.Debtors, -Property) %>% 
  glm(good~.,family=binomial,data=.)
Anova(logit.fit1)
```
```{r}
logit.fit1 <- testDF %>% 
  select (-ResidenceDuration, -Age, -Job.Type, -NumberPeopleMaintenance, -Telephone, -NumberExistingCredits, -Other.Debtors, -Property, -Credit.History) %>% 
  glm(good~.,family=binomial,data=.)
Anova(logit.fit1)
```
```{r}
logit.fit1 <- testDF %>% 
  select (-ResidenceDuration, -Age, -Job.Type, -NumberPeopleMaintenance, -Telephone, -NumberExistingCredits, -Other.Debtors, -Property, -Credit.History, -Savings) %>% 
  glm(good~.,family=binomial,data=.)
Anova(logit.fit1)
```
```{r}
logit.fit1 <- testDF %>% 
  select (-ResidenceDuration, -Age, -Job.Type, -NumberPeopleMaintenance, -Telephone, -NumberExistingCredits, -Other.Debtors, -Property, -Credit.History, -Savings, -Amount) %>% 
  glm(good~.,family=binomial,data=.)
Anova(logit.fit1)
```
```{r}
logit.fit1 <- testDF %>% 
  select (-ResidenceDuration, -Age, -Job.Type, -NumberPeopleMaintenance, -Telephone, -NumberExistingCredits, -Other.Debtors, -Property, -Credit.History, -Savings, -Amount, -Personal.Status) %>% 
  glm(good~.,family=binomial,data=.)
Anova(logit.fit1)
```
# a. Comment on the model’s Residual deviance as compared to both the degrees of freedom and the Null deviance. Is this a “good” model for the prediction of Class based on these statistics alone?
Residual deviance is less than the Null deviance. Siginificant decrease in the null deviance. The p value is 5.606281e-11. The model is yes, since the p value is close to zero.

```{r}
summary(logit.fit1)
```
```{r}
253.67-159.08
```
```{r}
pchisq(94.59,df=199-177,lower.tail = FALSE)
```

# b. Which of the coefficients are most significant?
Duration, Checking, Employment.Duration
Duration - for every increase in one unit of Duration, the odds of Good decrease proportionally by a multiplying the number by 0.9418022. 
Checking - everything is in reference to Checking 0.to.200 group.
```{r}
exp(-0.05996)
```
```{r}
table(GermanCredit$Checking)
```
```{r}
0.93248, -1.32789, 0.80624
```


#c. Interpret, in plain english, the Duration and Amount coefficients. How do they effect our prediction of the Class variable.
The Amount has been removed and has noe effect on the model.

#d. Interpret, in plain english, the Intercept coefficient of this model. Remember that the Intercept in logistic regression is subject to the same interpretation of factor variables as linear regression.
